\begin{acknowledgments}
\noindent This dissertation would have never been possible without all the supports from my family, friends, and mentors.
I am afraid I have to limit to a few highlights. 
I am indebted to my dissertation advisor Ivan Deutsch, from whom I find friendship, knowledge, wisdom, and encouragement.  
Ivan is one of those physicists who think not only about research itself but also pay a lot of attentions to advancing students via inspiring teaching, thoughtful spiritual supports and stable funding supports. 
The freedom and trust he granted to me are the highest privilege and invaluable treasure to me to contemplate about the big picture of the field and ask important questions into future.
With his supports, I can focus on my research and help the scientific community and our collaborators conquer the biggest theoretical barriers ahead without worrying about writing small and fast papers in limited time periods. 
The opportunities---including but not limited to---of questioning, trying and failing, pinpointing down concrete ideas, coordinating with our collaborators and solving the theoretical problems with a proof-of-principle demonstration are the best touchstone for me to grow my confidence of conducting independent and collaborative researches for my long-term adventure. 
Moreover, Ivan has taught me how to intuitively think about physics instead of blindly following math, which extinguishes my aversion towards the uncertain research path that can hardly be described in math. 

I am owing to Prof. Baoxun Du, who I may not have a chance to see again yet have significantly infected me with his passion and dedication of creating new knowledge and passing it to younger generations; 
my parents, Yuanjie Qi and Tinghui Fu, for their understanding and encouragement to me to finish my degree study oversea; 
Prof. Carl Caves and Prof. Akimasa Miyake, who introduced me to the broad field of quantum information and quantum computing; 
Prof. Poul Jessen, for his excellent insight on my research subject from the experimental side; 
Prof. Sudahka Prasad and Prof. Alejandro Manjavacas, who supported me as if I were their own student; 
Prof. Yuan-Yu Jau and Dr. Jongmin Lee at the Sandia National Labs and Perry Rice at the Miami University, with whom I had very pleasant and fruitful collaborations; 
Prof. Arash Mafi, who provided me helpful feedbacks and advices for my studies and presentations; 
Prof. Elohim Becerra, with whom I always feel comfortable to knock the door and ask possibilities of experimental implementations of my naive theoretical ideas and extending collaborations with his experimental colleagues elsewhere. 
I am also grateful to Dr. Pablo Solano, now, at MIT, and Prof. Lius Orozco at the University of Maryland for their stimulating discussions on the mechanical oscillations of atoms due to the launch of a probe they observed in labs, which eventually inspired me to think about the direction on minimizing the disruption of the probe light to the atoms as a part of my dissertation work. 

Many thanks to Ben Baragiola, from whom I learned the essential of quantum measurement and how to conquer a big research subject by dividing it into solvable pieces; 
Josh Combes, who was my role model as an excellent researcher and was always willing to answer my questions any time; 
Ninnat (Tom) Dangniam and Matt Chase, who were my most reliable lunch/dinner mates and shared their time and opinions with me on every corner of my life; 
Ezad Shojaee, who thought most seriously on our countless questions to him; 
Jonathan Gross and Anupam Mitra, who shared the common interests and passion with me in programming and beyond; 
Raf Alexander, who was very generous to give me advice on academia and writing; 
Qufei Gu, Zhixian Yu, Lewis Chiang, Nan Li, Xijie Luo, Lei Ma and Ning Hsu, who made me home with frequent ride offerings, gatherings and cheers; 
Adrian Chapman, James Hendrie, Akram Etemadi Amin, Karishma Bansal, Anirban Chowdhury, Sayonee Ray, Maria (Mariami) Gachechiladze and Davide Orsucci, who made my life in Albuquerque full of surprises and relaxing entertainments; 
Leigh Norris, from whom I learned the details about spin squeezing that I couldn't find elsewhere, and received very kind cares and the joy of interacting with her dog, the little ``sunny bird''; 
Bob Keating, Charlie Baldwin, Robert Cook, Amir Kalev, Gopi Muraleedharan, and Karthik Chinni, who supported me as group members in all aspects; 
Travis Scholten, whose standard on colormaps and presentations was a luxury for me to reach but a significant topic to learn; 
Zhang Jiang, who taught me driving and advised me like a big brother; 
Jacob Miller, an aloha-attired friend who occasionally spoke Chinese with me and warmly reminded me not to stay too late in the office; 
Robin Blume-Kohout, who inspired me with better presentation styles; 
Andy Ferdinand, Satomi Sugaya and Mohamad Fazel, who made my last sweet home in Albuquerque and filled my hungry stomach with perfect food; 
and the rest of current or former CQuIC people---Chris Jackson, Chris Cesare, Chris Ferrie, Matthias Lang, Pablo Poggi, Ciaran Ryan-Anderson, Shashank Pandey, Akash Rakholia, Nathaniel Ristoff, Matthew DiMario, Matthew Curry, and Rolando Somma for sharing the enthusiasm with me in quantum information.

I also thank Gloria Cordova and Vicky Bird for booking flights and hotels and for helping me on countless tiny yet important office things; 
Alisa Gibson for all the paperworks and administrative reminders that I couldn't imagine how she has successfully managed and saved me from disasters time and time again; 
Tom Hess and Leanne Yanabu, who helped me a lot on computer and website stuff; 
Gary Harrison and Steve Portillo, who fixed small but annoying problems in the office promptly, like blinking light bulbs, leaking pipes and broken lockers, to create a comfortable working environment for me; 
and Linda Melville for helpful advice about living and studying in the \hbox{US} as my international student advisor.

In writing this dissertation, I have received careful and prompt proofreads and edits from Ninnat (Tom), Johar Ashfaque (at Max-Planck-Institute), Satomi, Andy, and Joshua Teves (on Reddit), beside my committee.
Without their help, this dissertation could not be finished in time. I would like to thank them from the heart.

I may not have much to return to everyone individually, but persisting my passion and endeavor that, I believe, will advance the community towards our common destiny is the journey I will continue on.
\end{acknowledgments} 
